HBCC - DLPFC - FEATURECOUNTS - GRCh38 - CQN - Sparse Model

### 2019-12-17 cmc-rnaseq-de/HBCC_DLPFC_FEATURECOUNTS_GRCh38_CQN_Sparse.Rmd
fix file relative path

knit2synapse::createAndKnitToFolderEntity(file = "./HBCC_DLPFC_FEATURECOUNTS_GRCh38_CQN_Sparse.Rmd",
                                          parentId ="syn21435176",
                                          folderName = 'HBCC - DLPFC - FEATURECOUNTS - GRCh38 - CQN - Sparse Model')
```

>>>>

knit2synapse::createAndKnitToFolderEntity(file = "./cmc-rnaseq-de/HBCC_DLPFC_FEATURECOUNTS_GRCh38_CQN_Sparse.Rmd",
                                          parentId ="syn21435176",
                                          folderName = 'HBCC - DLPFC - FEATURECOUNTS - GRCh38 - CQN - Sparse Model')
```
